R Notebook

### 2017-08-01 doc/RMD/wmn-differentiation.Rmd
export AMOVA table

```{r AMOVA-nomex, cache = TRUE}
datnomex <- setPop(dat11cc, ~Region) %>% popsub(blacklist = "Mexico")
bdnm     <- bruvo.dist(datnomex, replen = other(datnomex)$REPLEN)
ssc_amova_nm <- poppr.amova(datnomex, ~SourceType/Region, dist = bdnm, quiet = TRUE)
ssc_amova_nm_test <- randtest(ssc_amova_nm, nrepet = 999)
plot(ssc_amova_nm_test)
(ssc_amova_nm_table <- make_amova_table(ssc_amova_nm, ssc_amova_nm_test))
```

```{r AMOVA_table, comment = NA}
make_amova_printable(ssc_amova_table, ssc_amova_nm_table) %>%  
  as_tibble() %>%
  add_column(Hierarchy = c("Between Source", "Between Region within Source", "Within Region"), .before = 1) %>%
  rename(ps = `Phi statistic`) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  rename(`$\\Phi statistic$` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  select(-P) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(1.3, 0.7, 0.9, 1, 1.3)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:5, "center") %>% 
  huxtable::print_md(max_width = 95)
```

@@

```{r wmndapc, cache = TRUE}
filter <- strata(dat11cc) %>%
  group_by(Region) %>%
  mutate(filter = length(unique(SourceType)) > 1) %>%
  pull(filter)
wmn_compare <- dat11cc[filter]
set.seed(2017-07-12)
wmndapc <- xvalDapc(tab(wmn_compare), pop(wmn_compare), n.rep = 200, n.pca = 1:10)
wmndapc
scatter(wmndapc$DAPC)
(wmntab <- table(wmndapc$DAPC$assign, wmndapc$DAPC$grp))
chisq.test(wmntab, simulate.p.value = TRUE)
```

@@

ggcompoplot::ggcompoplot(bebug_dapc, setPop(bebug, ~Region), cols = 5, pal = viridis::plasma(3, end = 0.85)) +
  theme(legend.position = "top")
```

>>>>

```{r AMOVA-nomex, cache = TRUE}
datnomex <- setPop(dat11cc, ~Region) %>% popsub(blacklist = "Mexico")
bdnm     <- bruvo.dist(datnomex, replen = other(datnomex)$REPLEN)
ssc_amova_nm <- poppr.amova(datnomex, ~SourceType/Region, dist = bdnm, quiet = TRUE)
ssc_amova_nm_test <- randtest(ssc_amova_nm, nrepet = 9999)
plot(ssc_amova_nm_test)
(ssc_amova_nm_table <- make_amova_table(ssc_amova_nm, ssc_amova_nm_test))
```

```{r AMOVA_table, comment = NA}
make_amova_printable(ssc_amova_table, ssc_amova_nm_table) %>%  
  as_tibble() %>%
  add_column(Hierarchy = c("Between Source", "Between Region within Source", "Within Region"), .before = 1) %>%
  readr::write_csv(path = file.path("results", "tables", "AMOVA-region.csv"), col_names = TRUE) %>%
  rename(ps = `Phi statistic`) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  mutate(ps = case_when(Hierarchy == "Between Source" ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi statistic$` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  select(-P) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(1.1, 0.6, 0.9, 0.9, 1.4)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:5, "center") %>% 
  huxtable::print_md(max_width = 100)
```

@@

```{r wmndapc, cache = TRUE}
filter <- strata(dat11cc) %>%
  group_by(Region) %>%
  mutate(filter = length(unique(SourceType)) > 1) %>%
  pull(filter)
wmn_compare <- dat11cc[filter]
set.seed(2017-07-12)
wmndapc <- xvalDapc(tab(wmn_compare), pop(wmn_compare), n.rep = 200, n.pca = 1:10)
wmndapc$DAPC
scatter(wmndapc$DAPC)
(wmntab <- table(wmndapc$DAPC$assign, wmndapc$DAPC$grp))
chisq.test(wmntab, simulate.p.value = TRUE)
```

@@

ggcompoplot::ggcompoplot(bebug_dapc, setPop(bebug, ~Region), cols = 5, pal = viridis::plasma(3, end = 0.85)) +
  theme(legend.position = "top")
apply(bebug_dapc$posterior, 2, mean)
```
